---
title: "Making Graphs in R Using ggplot2: Quiz & Exercises"
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
    df_print: default
runtime: shiny_prerendered
description: >
  Learn about the basic syntax of R.
---

```{r setup, include=FALSE}
library(learnr)
library(ggplot2)
tutorial_options(exercise.timelimit = 10)
Pulse<-readRDS("Pulse.RDS")

```


## Quiz 

*Question 1*
```{r Q1, echo=FALSE}
question("Which part of the ggplot code specifices the mapping of columns from the data onto different attributes of the plot?",
  answer("aesthetic",correct=TRUE),
  answer("geom"),
  answer("theme"),
  answer("scale"),allow_retry = TRUE,random_answer_order = TRUE
)
```



*Question 2*

```
ggplot(data=Pulse,aes(x=Age))+
geom_hist()


```

```{r Q2, echo=FALSE}
question("Why have I got an error from trying to run the code above?",
  answer("Age is a categorical variable in the data so cannot be plotted in a histogram",message="There is a categorical variable in the data for Age, but this is called 'AgeGrp'. Age is a continuous variable"),
  answer("The function should be 'geom_histogram' not 'geom_hist'",correct=TRUE),
  answer("There are too many brackets being closed at the end of the first line of code"),
  answer("geom_hist requires a y aesthetic"),allow_retry = TRUE,random_answer_order = TRUE
)
```


*Question 3*

```{r}
ggplot(data=Pulse,aes(x=PoliticalParty))+
  geom_bar()
```

```{r Q3, echo=FALSE}
question("I have written the code above to produce a bar chart of the frequency of policital party of the respondents. I would like to make the bar for 'Democrat' appear shaded in blue, 'Independent' shaded in grey and 'Republican' shaded in red. What part(s) of my code should I modify?",
  answer("Include 'colour=c('blue','grey','red') within the geom_bar line"),
  answer("Include 'fill=c('blue','grey','red') within the geom_bar line"),
  answer("Include 'colour=PoliticalParty' within the aesthetic and add an extra line using scale_colour_manual"),
  answer("Include 'fill=PoliticalParty' within the aesthetic and add an extra line using scale_fill_manual",correct=TRUE),allow_retry = TRUE,random_answer_order = TRUE
)
```


*Question 4* 
 
 
```{r q4_plot,echo=FALSE}

ggplot(data=Pulse,aes(x=PoliticalParty))+
  geom_bar()+
    facet_wrap(~Gender)
```
 
 
```{r Q4, echo=FALSE}


question("What code was used to produce the graph above?",
  answer(paste("ggplot(data=Pulse,aes(x=PoliticalView))","geom_bar()","facet_wrap(~Gender)<br>",sep="<br>")),
  answer(paste("ggplot(data=Pulse,aes(x=PoliticalParty))","geom_barchart()","facet(~Gender)<br>",sep="<br>")),
  answer(paste("ggplot(data=Pulse,aes(x=PoliticalView)) +","geom_barchart() +","facet_wrap(Gender)<br>",sep="<br>")),
  answer(paste("ggplot(data=Pulse,aes(x=PoliticalParty)) +","geom_bar() +","facet_wrap(~Gender)<br>",sep="<br>"),correct=TRUE),allow_retry = TRUE,random_answer_order = TRUE
)
```
``


## Exercises  

**Exercise 1. Fix the error(s) in this code to produce a boxplot of attractiveness by age group**

```{r ex1,exercise=TRUE,error=TRUE}
ggplot2(data = Pulse,  aes(x = agegroup, y = attractiveness) 
  geom_boxplot()
```

**Exercise 2. Produce a bar chart showing the frequencies of the Race variable**

```{r ex2,exercise=TRUE}

```

**Exercise 3. Continuing the previous example, use facets to make separate bar charts of race by political party**

```{r ex3,exercise=TRUE}

```

**Exercise 4. Produce a set of boxplots of attractiveness by age group, with separate panels for each gender. Use some colours and add sensible titles and labels**

```{r ex4,exercise=TRUE}

```

**Exercise 5. Produce a graph to investigate whether there is a relationship between income, on the y axis, and attractiveness, on the x axis. Use different colours for each political party, a log axis for income and add in some sensible titles and labels. You also might want to consider using more than one layer.**

```{r ex5,exercise=TRUE}
```


Solutions to these exercises will be made available when the next module of the course becomes live. Check the course site for details. 

## Appendix: 'Pulse' dataset 

The data we are using in this session is an extract of a survey conducted in the US in June 2018, as part of the Pulse of the Nation series of surveys. This survey was a representative sample of the American population. You can read more about the survey (and others from the same series) <a href="https://thepulseofthenation.com" target="_blank">here</a>. The data has been cleaned and edited slightly for use in this course.

The dataset contains an extract of 356 responses to 10 of the survey questions, and has been imported to R as a data frame called `Pulse`.

A summary of the columns in the dataset is below.

```{r, echo=FALSE,message=FALSE,warning=FALSE}
library(tidyverse)
library(knitr)

data.frame(Column=c("Gender","Age","AgeGrp","Race","Income","Education","PoliticalParty","PoliticalView","ApproveTrump","Attractiveness"),
           Description=c("What gender do you identify with?","What is your age?","Age range","What is your race?",
                         "About how much money do you make per year? (USD)","What is your highest level of education?",
                         "In politics today, do you consider yourself a Democrat, a Republican, or Independent?",
                         "Would you say you are liberal, conservative, or moderate?",
                         "Do you approve, disapprove, or neither approve nor disapprove of how Donald Trump is handling his job as president?",
                        "On a scale of 1-10, how physically attractive do you consider yourself?")) %>% kable()

```


```{r,echo=FALSE}
DT::datatable(Pulse)
```

(You can use the arrow keys on your keyboard to scroll right in case the data table does not fit entirely on your screen)

## Appendix:  Useful reference links  

R Graphics Cookbook: <a href="http://www.cookbook-r.com/Graphs/" target="_blank">http://www.cookbook-r.com/Graphs/</a> 

ggplot2 CheatSheet:<a href="https://rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf" target="_blank">https://rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf   </a>  

R Color Chart: <a href="http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf" target="_blank">http://www.stat.columbia.edu/~tzheng/files/Rcolor.pdf     </a>   

ggplot2 manuals (warning - technical and slightly pretentious. First line "ggplot2... embodies a deep philosophy of visualisation"): <a href="https://ggplot2.tidyverse.org/" target="_blank">https://ggplot2.tidyverse.org/     </a>     

Plotting with ggplot - Roger Peng videos:
<a href="https://www.youtube.com/watch?v=HeqHMM4ziXA" target="_blank">Part 1    </a>  
<a href="https://www.youtube.com/watch?v=n8kYa9vu1l8" target="_blank">Part 2 </a>  

